---
title: "Class11"
date: "2026-30-16"
output:   
  html_document:
  toc: true
  toc_float: true
  number_secitons: true
  code_download: true
  code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives

- Enable you to scrape multiple webpages (from the same site), using a for loop type approach 

- Enable you to scrape multiple webpages (from the same site), using thee [purrr](https://purrr.tidyverse.org/) which is a functional programming approach

## Re-Examining the bulletin example 

Let us try to expand on the example from last class to include the following: 
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/), [BUS](https://bulletin.miamioh.edu/courses-instruction/bus/),
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and [MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/).


**Comment:** We will follow the **DRY Principle**, which stands for **Don't repeat yourself**.

```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')


courses_df = data.frame() # initializing a container to store stuff in the loop
for (abbrv in dept_abbrv) {
  cat(rep("-", 50) , "\n" )
  print(abbrv)
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  print(df$title[1:2])
  courses_df = rbind(courses_df, df)
}

```


## 'purrr' approach for the same problem

- Functional programming approach, we will write our own function. In r we use the function called 'function' to create a function. As opposed to fuction r functions return a single object. 

```{r purrr approach}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

# This function takes an aggregation as an input and returns a data frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
    'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
  )
  
  webpage = rvest::read_html(bulletin_url)
  
  webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
  webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv = 'eco')

# To use functions from purrr, we will use a map_() function or a map2_() function
# Map uses function that takes a single input (or you are changing a single input)
# Map2 uses a function that takes two inputs
# pmap >=3
# After the _ you put the type of object you want returned
# .x is the vector we will iterate over 
# .f is the function we will use

courses_df_from_purr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```

## Scrape data using from the website planecrashinfo

The website that we want to scrape is called <https://www.planecrashinfo.com/> and it contains a database of plane crashes by year 

```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')

crash_page = rvest::read_html(crash_url)
```


